\textbf{Emergency Service Location Optimization in a Multi-Zone County based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
Add 2.2

\usepackage{url}
% \usepackage{fullpage}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{float}
\restylefloat{table}
\restylefloat{figure}
\usepackage{setspace}
% \usepackage{minted}
% \usemintedstyle{colorful}
\graphicspath{{./Pictures/}}

@@

\section{Assumptions and Justifications}
\begin{description}
    \item[TODO(drew): Add these assumptions] \hfill \\
    	* Each zone is not a point, but rather a distribution. We experimented with...
        * Route frequency is correlated with population frequency (two random variables?)
    \item[1. Naming] \hfill \\
    	A county is another name for a county. ... TODO(drew)
        Travel...
    \item[2. Zone to Zone Travel] \hfill \\
    	The travel times given are considered to be optimal routes from the center of one zone to
        the center of the another, regardless of any other zones that may lie in between.
    \item[3. Travel Inside Each Zone] \hfill \\
    	The travel times given for travel from any zone to itself is the average
        of all the travel times of the different routes within that zone.
    \item[4. Directional Travel Inside Each Zone] \hfill \\
    	The ratio between the time it takes inside a zone to travel toward a second zone,
        to the time it takes inside a zone to return from a second, is equal to the ratio
        between the travel time from the first zone to the second, and the travel time from the
        second to the first.
    \item[5. Ambulance Placement] \hfill \\
        Ambulances can only be placed in the very center of a zone. Because we do not know the
        spacial position of the zones relative to each other, we cannot consider the ambulances
        being closer to one zone or another.
    \item[6. Partial Coverage] \hfill \\
        Partial ambulance coverage of a zone will be treated as incomplete even coverage over the entire
        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
        that multiple ambulances will cover different areas of the zones, thus evening out coverage.
        (If partial coverages from multiple ambulances sum to above the total population of a zone,
        we assume that zone is completely covered by the ambulances.)
\end{description}

@@

\subsection{Zone-to-Zone Population Dynamics}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct),
will be hereafter referred to as zone-to-zone coverage.

A lack of spatial understanding of the county entails the use of a different type of population density. Rather than expressing population as a function of area or distance, we chose to express population density in terms of travel time from a reference point. This is analogous to plotting the number of people a vehicle is likely to meet at each time as it drives along a one-dimensional path.

\begin{figure}
\centering
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{B(t).png}
  \caption{An example of a zone's population density as a function of travel time from another zone.}
  \label{fig:sub1}
\end{subfigure}%
\hfill
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{A(t)B(t).png}
  \caption{TODO(drew)}
  \label{fig:sub2}
\end{subfigure}
\label{fig:test}
\end{figure}

The population that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be referred to as zone-to-zone coverage.
\newpage

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3.5in]{A(t)B(t).png}
\caption{TODO(drew)}
\label{A(t)B(t)}
\end{center}
\end{figure}

\begin{description}
    \item[$\mathbf{A(t), B(t)}$] \hfill \\
    	Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
    \item[$\mathbf{Z_{AB}(t)}$] \hfill \\
    	Zone-to-zone coverage of B from A
    \item[$\mathbf{v}$] \hfill \\
    	Required ambulance response time
    \item[$\mathbf{T_{AB}}$] \hfill \\
    	Travel time from A to B, given
    \item[$\mathbf{T_{BA}}$] \hfill \\
    	Travel time from B to A, given
    \item[$\mathbf{P_B}$] \hfill \\
    	Total population of B
    \item[$\mathbf{F_B(s)}$] \hfill \\
    	The probability curve for differences in travel time within B
   \item[$\mathbf{T_A}$] \hfill \\
    	Average travel time inside of A
    \item[$\mathbf{T_{A+}}$] \hfill \\
    	Average travel time in the direction of B to A inside of A
    \item[$\mathbf{T_{A-}}$] \hfill \\
    	Average travel time in the direction of A to B inside of A
   \item[$\mathbf{T_B}$] \hfill \\
    	Average travel time inside of B
    \item[$\mathbf{T_{B+}}$] \hfill \\
    	Average travel time in the direction of A to B inside of B
    \item[$\mathbf{T_{B-}}$] \hfill \\
    	Average travel time in the direction of B to A inside of B
    \item[$\mathbf{a, b}$] \hfill \\
    	Width of A and B respectively
    \item[$\mathbf{g}$] \hfill \\
    	Width of the gap between A and B
\end{description}

%TODO: Graphical representation of origin and setup

The function for zone-to-zone coverage in respect to travel time can be written out as
$$Z_{AB}(t) = P_B \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$

In order to find the width of zone B, b, we can take the probability curve of differences in travel time within B,
$F_B(s)$, and find the average travel time within B. This is the average difference in travel time, and is equal to $T_{B+}$.
$$T_{B+} = \int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} s F_B(s) ds$$

The probability curve of differences in travel time within B, $F_B(s)$, can be found by performing a cross-correlation
of $B(t)$ on itself, with $s$ being the difference in travel time plotted against frequency.
$$P_B(s) =\int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} B(t) * B(t-s) dt$$

The average travel time in the direction of A to B inside of A, $T_{A-}$, and the average travel time in the direction of B to A
inside of A, $T_{A+}$, have a total average travel time of $T_A$. We can also write the ratio of $T_{A+}$ and $T_{A-}$,
which is equivalent to the ratio of $T_{BA}$ and $T_{AB}$. The same can be done with $T_{B}$.
$$T_A = \frac{T_{A+} + T_{A-}}{2}$$
$$\frac{T_{A+}}{T_{A-}} = \frac{T_{BA}}{T_{AB}}$$
$$\frac{T_{B+}}{T_{B-}} = \frac{T_{AB}}{T_{BA}}$$

This allows us to solve for $T_{A-}$  and $T_{B+}$.
$$T_{A-} = \frac {2T_A}{1+ \frac{T_{BA}}{T_{AB}}}$$
$$T_{B+} = \frac {2T_B}{1+ \frac{T_{AB}}{T_{BA}}}$$

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3in]{greedy6point.pdf}
\caption{Graph in fig. \ref{fig:fullgraph}, with edges longer than 8 minutes removed}
\end{center}
\end{figure}

@@

% \inputminted[fontsize=\footnotesize]{python}{../Code/optimizer.py}

>>>>

\usepackage{url}
% \usepackage{fullpage}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{float}
\restylefloat{table}
\restylefloat{figure}
\usepackage{setspace}
\usepackage{minted}
\usemintedstyle{colorful}
\graphicspath{{./Pictures/}}

@@

\section{Assumptions and Justifications}
\begin{description}
    \item[TODO(drew): Add these assumptions] \hfill \\
    	* Each zone is not a point, but rather a distribution. We experimented with...
        * Route frequency is correlated with population frequency (two random variables?)
    \item[1. Naming] \hfill \\
    	A county is another name for a county. ... TODO(drew)
        Travel...
        Travel times...
    \item[2. Zone to Zone Travel] \hfill \\
    	The travel times given are considered to be optimal routes from the center of one zone to
        the center of the another, regardless of any other zones that may lie in between.
    \item[3. Travel Inside Each Zone] \hfill \\
    	The travel times given for travel from any zone to itself is the average
        of all the travel times of the different routes within that zone.
    \item[4. Directional Travel Inside Each Zone] \hfill \\
    	The ratio between the time it takes inside a zone to travel toward a second zone,
        to the time it takes inside a zone to return from a second, is equal to the ratio
        between the travel time from the first zone to the second, and the travel time from the
        second to the first.
    \item[5. Ambulance Placement] \hfill \\
        Ambulances can only be placed in the very center of a zone. Because we do not know the
        spacial position of the zones relative to each other, we cannot consider the ambulances
        being closer to one zone or another.
    \item[6. Partial Coverage] \hfill \\
        Partial ambulance coverage of a zone will be treated as incomplete even coverage over the entire
        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
        that multiple ambulances will cover different areas of the zones, thus evening out coverage.
        (If partial coverages from multiple ambulances sum to above the total population of a zone,
        we assume that zone is completely covered by the ambulances.)
\end{description}

@@

\subsection{Zone-to-Zone Population Dynamics}
The population that an ambulance can cover in a second zone, B, from a first zone, A, will be referred to as zone-to-zone coverage. Zone-to-zone coverage also applies if A and B are the same zone, and represents the coverage of an ambulance in the zone it is stationed in.

A lack of spatial understanding of the county entails the use of a different type of population density. Rather than expressing population as a function of area or distance, we chose to express population density in terms of travel time from a reference point. This is analogous to plotting the number of people a vehicle is likely to meet at each time as it drives along a one-dimensional path. See Figure \ref{B(t)}.

\begin{figure}
\centering
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{B(t).png}
  \caption{An example of a zone's population density as a function of travel time from another zone.}
  \label{B(t)}
\end{subfigure}%
\hfill
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{A(t)B(t).png}
  \caption{The width of A and B are shown. $T_{AB} $ is the travel time between the centers (i.e. the provided average).}
  \label{A(t)B(t)}
\end{subfigure}
\caption{Examples of population density as a function of travel time}
\label{examples}
\end{figure}

\newpage

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3.5in]{6point.pdf}
\caption{A graph of the nodes (zones) and edges (travel times).}
\label{satan1}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3.5in]{greedy6point.pdf}
\caption{A graph of the nodes (zones) with all edges (travel times) greater than 8 removed.}
\label{satan2}
\end{center}
\end{figure}

%TODO: We are trying to find zone-to-zone coverage...

\begin{description}
    \item[$\mathbf{Z_{AB}(t)}$] \hfill \\
    	The zone-to-zone coverage function of B from A
    \item[$\mathbf{A(t), B(t)}$] \hfill \\
    	Probability density functions with respect to travel time from the center of A
    \item[$\mathbf{v}$] \hfill \\
    	Required ambulance response time
    \item[$\mathbf{T_{AB}}$] \hfill \\
    	Travel time from A to B, given
    \item[$\mathbf{T_{BA}}$] \hfill \\
    	Travel time from B to A, given
    \item[$\mathbf{P_B}$] \hfill \\
    	Total population of B
    \item[$\mathbf{F_B(s)}$] \hfill \\
    	The probability curve for differences in travel time within B
   \item[$\mathbf{T_A}$] \hfill \\
    	Average travel time inside of A
    \item[$\mathbf{T_{A+}}$] \hfill \\
    	Average travel time in the direction of B to A inside of A
    \item[$\mathbf{T_{A-}}$] \hfill \\
    	Average travel time in the direction of A to B inside of A
   \item[$\mathbf{T_B}$] \hfill \\
    	Average travel time inside of B
    \item[$\mathbf{T_{B+}}$] \hfill \\
    	Average travel time in the direction of A to B inside of B
    \item[$\mathbf{T_{B-}}$] \hfill \\
    	Average travel time in the direction of B to A inside of B
    \item[$\mathbf{a, b}$] \hfill \\
    	Width of A and B respectively
    \item[$\mathbf{g}$] \hfill \\
    	Width of the gap between A and B
\end{description}

%TODO: Graphical representation of origin and setup
% Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution

The function for zone-to-zone coverage in respect to travel time can be written as the product of the population of B with the percent of the population that is covered from A in less than $v$ minutes. The percent is the area under the probability curve, $B(t)$. As shown in Figure \ref{A(t)B(t)}, the bounds begin at $T_{AB} - \frac{b}{2}$ and end at $v$. If $v$ is less than $T_{AB} - \frac{b}{2}$, the coverage of B is 0.

$$Z_{AB}(t) = P_B \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$

$B(t)$ is a population density function with a zone-specific constant $b$, which is the width of zone B. Every zone has a different $b$ and, as a result, a different $B(t)$. In order to find this specific $B(t)$, we must obtain $b$. Until then, we cannot directly evaluate $B(t)$.

Using the average travel time within B that is provided to us, we can calculate the value for $b$. However, since we are provided with a general average travel time within each zone---which does not account for the direction of travel---we must extrapolate both the average travel time within B towards A and within B away from A.

The average travel time in the direction of A to B inside of B, $T_{B+}$, and the average travel time in the direction of B to A
inside of B, $T_{B-}$, have a total average travel time of $T_B$. We can also write the ratio of $T_{B+}$ and $T_{B-}$,
which is equivalent to the ratio of $T_{AB}$ and $T_{BA}$.
$$T_B = \frac{T_{B+} + T_{B-}}{2}$$
$$\frac{T_{B+}}{T_{B-}} = \frac{T_{AB}}{T_{BA}}$$

This allows us to solve for $T_{B+}$.
$$T_{B+} = \frac {2T_B}{1+ \frac{T_{AB}}{T_{BA}}}$$

Now that we have the average travel time within B away from A, we can set that equal to the definition of the average travel time within B away from A, as shown below, and solve for the $b$ originally sought. The definition is  the area under the distribution of all the possible travel times from one random point in B to another point in B.

$$T_{B+} = \frac {2T_B}{1+ \frac{T_{AB}}{T_{BA}}} = \int^b_0 s F_B(s) ds$$

To find this distribution of travel times, we take the cross correlation of $B(t)$ on itself, with $s$ being  travel time plotted against frequency.
$$F_B(s) =\int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} B(t) B(t-s) dt$$

Combining the previous two equations, we can finally solve for $b$ in terms of known values. $b$ is a zone-specific constant embedded within the general equation $B(t)$. Depending on the type of equation that $B(t)$ is, $b$ can be solved for in different ways.

$$\frac {2T_B}{1+ \frac{T_{AB}}{T_{BA}}} = \int^b_0 \int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} s B(t) B(t-s) dt ds$$

With $b$ solved and $B(t)$ fully defined, we can finally evaluate the original integral for zone-to-zone coverage.

$$Z_{AB}(t) = P_B \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3in]{greedy6point.pdf}
\caption{Graph in fig. 2, with edges longer than 8 minutes removed}
\end{center}
\end{figure}

@@

\inputminted[fontsize=\footnotesize]{python}{../Code/optimizer.py}
